Article 1:	Construct Validity and Correspondence of Google Trends

### 2022-02-23 paper1.Rmd
Some findings written

---
title: "Article 1:	Construct Validity and Correspondence of Google Trends"
author: "Kelsey Gonzalez"
date: "`r format(Sys.time(), '%d %B, %Y')`"
editor_options:
  chunk_output_type: console
  markdown: 
    wrap: 72
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    number_sections: true
  bookdown::word_document2: 
    toc: true
    reference_docx: StylesTemplate.docx
header-includes:
   - \usepackage{siunitx}
   - \usepackage{setspace}
   - \usepackage{dcolumn}
   - \usepackage{caption}
   - \usepackage{longtable}
   - \usepackage{booktabs}
   - \doublespacing
   - \usepackage{placeins}
csl: american-sociological-association.csl
bibliography: "thesis.bib"
indent: true
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      warning = FALSE,
                      cache = TRUE,
                      fig.width = 7,
                      fig.asp = 0.8,
                      out.width = "80%",
                      fig.align="center"
                      # dev.args = list(png = list(type = "cairo"))
                      )

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, glue, extrafont, here, jtools, psych,
               modelsummary, showtext, thematic, kableExtra, scales, nlme)

@@

stars <- function(p.value){
  unclass(symnum(p.value, 
                 corr = FALSE, 
                 na = FALSE, 
                 cutpoints = c(0, 0.001, 0.01, 0.05, 1), 
                 symbols = c("***", "**", "*", " ")))
}

```
```{r data}
vacc_hes <- read_rds(here('data', 'cleaned_data', 'vacc_hes.rds'))
mask <- read_rds(here('data', 'cleaned_data', 'mask.rds')) %>%  ungroup()
covid <- read_rds(here('data', 'cleaned_data', 'covid.rds'))
suicide <- read_rds(here('data', 'cleaned_data', 'suicide.rds'))
pres_2016 <- read_rds(here('data', 'cleaned_data', 'pres_2016.rds'))
pres_2020 <- read_rds(here('data', 'cleaned_data', 'pres_2020.rds'))

@@

<https://journals.sagepub.com/doi/10.1177/0894439316631043> § What
constructs might google trends capture and not capture well? Capture
attention but not attitudes

@@

```{r data-sources-table}
#| results='asis',
#| tab.cap = 'airquality dataset caption here'

data_sources <- tibble::tribble(
~Validated.Data.Source, ~Type, ~Dates, ~Google.Trends.Used,
"General Social Survey", "Cross-Sectional", "2010 - 2020", NA,

"Vaccine Hesitancy for COVID-19", "Cross-Sectional", "March 3 – 15, 2021", "covid conspiracy', 'COVID-19 vaccine', 'Coronavirus', 'Covid-19'",

"Mask-Wearing Survey Data", "Cross-Sectional", "July 2 - 14, 2020", "'Face Mask', 'Mask', 'Cloth Face Mask'",

 "Covid Rates", "Longitudinal", "Every Monday, 2020 - 2021", "'Covid-19', 'Coronavirus', 'Taste Loss', 'Smell Loss'",

"County Suicide Rates", "Longitudinal", "Yearly 2010-2020", "'Suicide', 'Depression',' Suicide Hotline'",

"American National Election Survey", "Cross-Sectional", "2020", NA,

"Presidential Election Results", "Cross Sectional", "2016 & 2020", "'Hilary Clinton', 'Donald Trump', 'Joe Biden'"
 )

data_sources %>% 
  kbl() %>%
  # group rows
  pack_rows("Behaviors and Attitudes", 1,3, background = '#bad7db', bold = T) %>% 
  pack_rows("Health", 4,5, background = '#bad7db', bold = T) %>% 
  pack_rows('Political', 6,7, background = '#bad7db', bold = T) %>% 
  # header style
  row_spec(0, background = my_palette[8], color = 'white', bold = T) %>% 
  #overall styling
  kable_styling(latex_options = c( "hold_position"), full_width = T)

@@

One measure of attitudinal indicators is the Vaccine Hesitancy for COVID-19
[@vaches_data]. The CDC uses the U.S. Census Bureau’s Household Pulse Survey
(HPS) and the 2019 American Community Survey (ACS) 1-year Public Use Microdata
Sample (PUMS) to measure U.S. residents’ intentions to receive the COVID-19
vaccine if available during May 26, 2021 – June 7, 2021. This dataset consists
of `r nrow(vacc_hes)` observations, one for each U.S. County.

<!-- TODO: VARIABLE SCALE -->

Another attitudinal indicator I use is the Mask-Wearing Survey Data conducted by
Dynata for the New York Times from July 2 through 14, 2020 [@mask_data]. 250,000
survey respondents were asked, "How often do you wear a mask in public when you
expect to be within six feet of another person?". The NYT weighted each response
to create a county level measure of what percent of the county never, rarely,
sometimes, frequetly, and always wore a mask when in public. This dataset
consists of `r nrow(mask)` observations, one for each U.S. County.

<!-- TODO: VARIABLE SCALE -->

@@

I first use U.S. Covid-19 rates to validate health and disease related topics. I
retrieve U.S. county-level Covid-19 rates from by @covid_data, who compile this
data based on reports from state and local health agencies. It is widely
acknowledged that there are biases in this data due to inconsistencies and
availability in testing as well as different community propensity to test
[@gu22; @cdc20a] However, it is the best measure we have of actual case rates.
Case Rate is measured as number of cases per 100,000 population. Observations
vary from a minimum of 0 to a maximum of `r max(covid$covid_rate)` for each 
Monday from `r glue("{format( min(covid$date), '%B %d, %Y')} through {format(max(covid$date), '%B %d, %Y')}")`.
There are `r nrow(covid)` cases across `r nrow(count(covid, fips))` 
counties and `r nrow(count(covid, date))` dates. Missing data were interpolated 
using `zoo::na.approx()` [@zoo].

<!-- TODO: VARIABLE SCALE -->

I also use county-level suicide rates from the US Centers for Disease Control
and Prevention [-@suic_data]. Data is grouped by year from 2010-2020. Raw death
rates are scaled by population size for each year. There are `r nrow(suicide)` 
total cases, resulting from `r nrow(count(suicide, year))` observations of 
`r nrow(count(suicide, fips))` counties. Missing data were interpolated 
using `zoo::na.approx()` [@zoo].

<!-- TODO: VARIABLE SCALE -->

### political
Finally, I test Google Trends as an operationalization of political
attitudes by first looking at actual voting outcomes in historical US
Presidential Election results. This data comes from @pres_data, who scraped the
results from Townhall.com, Fox News, Politico, and the New York Times. Data on 
presidential outcomes were avaiable for `r nrow(pres_2016)` counties in 2016 and
`r nrow(pres_2020)` counties in 2020.

<!-- TODO: VARIABLE SCALE -->

@@

<!-- TODO: VARIABLE SCALE -->

@@

In addition to specific outcomes of interest, I also gathered various county
controls to investigate possible variable confounding. The first Seven of these
variables come from the 2010-2019 5-year American Community Surveys [@acs2019;
@acs2018; @acs2017; @acs2016; @acs2015; ; @acs2014; @acs2013; @acs2012;
@acs2011; @acs2010]. These data include total population, population density,
unemployment rate for those 16 and over, median county income, average commute
time, percent of households living under the poverty line, and percent above 65
years old. In addition, some models employ the U.S. Current Population Survey &
American Community Survey Geographic Estimates of Internet Use, 1997-2018
[@internet_use] to estimate households with broadband internet subscriptions.
This final variable is an attempt to capture the latent propensity to use the
internet for information search.

@@

## Analysis
For cross-sectional numeric data, I use the Pearson correlation formula (formula
\@ref(eq:pearsoncorr)) to calculate the strength of the relationship between
each Google Trend and the respective datasource.

@@

To address longitudinal correlations, I employ Repeated Measures Correlation
using the `rmcorr` package in R [@bland1995; @bakdash2017]. Repeated Measures
Correlation is useful for determining the within-county association for paired
measures across time and counties.

As an additional test of the relationships, I employ multiple linear regression
to identify the strength of relationships across locales: I include city-data
like county population size, broadband rates, and median income to attempt to
disentangle possible confounders of the relationship between Google search
Trends and verified indicators. Identifying these possible confounded
relationships will help to explain why some articles find relationships between
the trends and outcomes while others did not. For linear regression models, I
normalize independent variables, i.e.variables have been centered and scaled to
have a mean of 0 and standard deviation 1.

@@

## Cultural

```{r vacc_hes_analysis1}
tribble(
  ~'measure',~'covid_conspiracy', ~'covid_19_vaccine', ~'coronavirus', ~'covid_19', 
  "vacc_hes, Pearson's R Correlation",
  cor(vacc_hes$vacc_hesitant, vacc_hes$covid_conspiracy, use = "complete.obs"),
  cor(vacc_hes$vacc_hesitant, vacc_hes$covid_19_vaccine, use = "complete.obs"),
  cor(vacc_hes$vacc_hesitant, vacc_hes$coronavirus, use = "complete.obs"),
  cor(vacc_hes$vacc_hesitant, vacc_hes$covid_19, use = "complete.obs")
)  %>% 
  kbl(digits=4) %>%
  #overall styling
  kable_styling(latex_options = c( "hold_position"), full_width = T)
```

```{r vacc_hes_analysis2}
vacc_hes <- vacc_hes %>% 
  select(-c(DMA_google, Geo_QName)) %>% 
  mutate(across(covid_conspiracy:broadband  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))

@@

modelsummary(list(vacc_hes_1, vacc_hes_2, vacc_hes_2b,vacc_hes_3), 
             # title = "Linear Regression Results for Vaccine Hesitancy",
             notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).'),
             estimate = "{estimate}{stars}",
             gof_omit = 'AIC|BIC|ICC|RMSE'
             ) %>%
  kable_styling(latex_options = c("hold_position", 'condensed'),
                font_size = 8)

@@

pearson correlations
rsquared
coefficients
conclusion

```{r mask_analysis1}
tribble(
  ~'measure',~'face_mask', ~'mask', ~'cloth_face_mask',  
  "Mask Rare, Pearson's R Correlation",
  cor(mask$mask_rare, mask$face_mask, use = "complete.obs"),
  cor(mask$mask_rare, mask$mask, use = "complete.obs"),
  cor(mask$mask_rare, mask$cloth_face_mask, use = "complete.obs")
)  %>% 
  kbl(digits=4) %>%
  #overall styling
  kable_styling(latex_options = c( "hold_position"), full_width = T)
```

```{r mask_analysis2}
mask <- mask %>% 
  select(-c(DMA_google, Geo_QName)) %>% 
  mutate(across(face_mask:broadband  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))

@@

modelsummary(list(mask_1, mask_2, mask_3), 
             # title = "Linear Regression Results for Rare Mask Usage",
             notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).'),
             estimate = "{estimate}{stars}",
             gof_omit = 'AIC|BIC|ICC|RMSE') %>%
  kable_styling(latex_options = c("hold_position", 'condensed'),
                font_size = 8)

@@

```{r covid_analysis1}
covid_corrs <- read_rds(here('data', 'from_hpc', 'covid_corrs.rds'))
# covid_corrs[1,1] <- "Covid Rate, Pearson's R Correlation"
# write_rds(covid_corrs, here('data', 'from_hpc', 'covid_corrs.rds'))

covid_corrs %>% 
  kbl(digits=4) %>%
  #overall styling
  kable_styling(latex_options = c( "hold_position"), full_width = T)
```

```{r covid_analysis2}
covid <- covid %>% 
  select(-c(dma_google, Geo_QName, county, state)) %>% 
  mutate(across(covid_19:broadband  , ~ scale(.x, center=TRUE, scale=TRUE)[,1])) %>% 
  left_join(covid %>%
              group_by(fips) %>%
              summarize(covid_rate_fips_mean = mean(covid_rate, na.rm = TRUE)),
            by = "fips") %>% 
  drop_na(covid_rate)

@@

modelsummary(list(covid_1, covid_2, covid_3), 
             # title = "Hierarchical Model for Covid Case Rates",
             notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
                      'Random intercept per county'),
             estimate = "{estimate}{stars}",
             gof_omit = 'AIC|BIC|ICC|RMSE') %>%
  kable_styling(latex_options = c("hold_position", 'condensed'),
                font_size = 8)

@@

```{r suicide_analysis1}
suicide_corrs <- read_rds(here('data', 'from_hpc', 'suicide_corrs.rds'))

# suicide_corrs[1,1] <- "Death by Suicide Rate, Pearson's R Correlation"
# suicide_corrs[2,1] <- "Death by Suicide Rate, rmcorr"
# 
# write_rds(suicide_corrs, here('data', 'from_hpc', 'suicide_corrs.rds'))

suicide_corrs %>% 
  kbl(digits=4) %>%
  #overall styling
  kable_styling(latex_options = c( "hold_position"), full_width = T)
```

```{r suicide_analysis2}
suicide <- suicide %>% 
  select(-c(dma_google, Geo_QName, county, population, deaths)) %>% 
  mutate(across(suicide:broadband  , ~ scale(.x, center=TRUE, scale=TRUE)[,1])) %>% 
  left_join(suicide %>%
              group_by(fips) %>%
              summarize(death_rate_fips_mean = mean(death_rate , na.rm = TRUE)),
            by = "fips") %>% 
  drop_na(death_rate )

@@

modelsummary(list(suicide_1, suicide_2, suicide_3), 
             # title = "Hierarchical Model for Suicide Rates",
             notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
                      'Random intercept per county'),
             estimate = "{estimate}{stars}",
             gof_omit = 'AIC|BIC|ICC|RMSE') %>%
  kable_styling(latex_options = c("hold_position", 'condensed'),
                font_size = 8)

@@

```{r pres_2016_analysis1}
tribble(
  ~'measure',~'Searches for Hilary Clinton', ~ 'Searches for Donald Trump',
  "Votes for Clinton, Pearson's R Correlation",
  cor(pres_2016$clinton_p, pres_2016$`Hilary Clinton`, use = "complete.obs"),
  cor(pres_2016$clinton_p, pres_2016$`Donald Trump`, use = "complete.obs"),

  "Votes for Trump, Pearson's R Correlation",
  cor(pres_2016$trump_p, pres_2016$`Hilary Clinton`, use = "complete.obs"),
  cor(pres_2016$trump_p, pres_2016$`Donald Trump`, use = "complete.obs"),
)  %>% 
  kbl(digits=4) %>%
  #overall styling
  kable_styling(latex_options = c( "hold_position"), full_width = T)
```

```{r pres_2016_analysis2}
pres_2016 <- pres_2016 %>% 
  select(-c(Geo_QName, dma)) %>% 
  mutate(across(c(`Hilary Clinton`,`Donald Trump`:broadband)  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))

@@

```{r pres_2020_analysis1}
tribble(
  ~'measure',~'Searches for Joe Biden', ~ 'Searches for Donald Trump',
  "Votes for Biden, Pearson's R Correlation",
  cor(pres_2020$biden_p, pres_2020$`Joe Biden`, use = "complete.obs"),
  cor(pres_2020$biden_p, pres_2020$`Donald Trump`, use = "complete.obs"),

>>>>

---
title: "Article 1:	Construct Validity and Correspondence of Google Trends"
author: "Kelsey Gonzalez"
date: "`r format(Sys.time(), '%d %B, %Y')`"
editor_options:
  chunk_output_type: console
  markdown: 
    wrap: 72
output:
  bookdown::pdf_document2: 
    latex_engine: xelatex
    number_sections: true
  # bookdown::word_document2: 
  #   toc: true
  #   reference_docx: StylesTemplate.docx
header-includes:
   - \usepackage{siunitx}
   - \usepackage{setspace}
   - \usepackage{dcolumn}
   - \usepackage{longtable}
   - \usepackage{caption}
   - \usepackage{booktabs}
   - \usepackage{placeins}
   - \doublespacing
csl: american-sociological-association.csl
bibliography: "thesis.bib"
indent: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      warning = FALSE,
                      cache = TRUE,
                      fig.width = 7,
                      fig.asp = 0.8,
                      out.width = "80%",
                      fig.align="center"
                      )

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, glue, extrafont, here, jtools, psych,
               modelsummary, showtext, thematic, kableExtra, scales, nlme,
               flextable)

@@

```
```{r data}
vacc_hes <- read_rds(here('data', 'cleaned_data', 'vacc_hes.rds'))
mask <- read_rds(here('data', 'cleaned_data', 'mask.rds')) %>%  ungroup()
covid <- read_rds(here('data', 'cleaned_data', 'covid.rds'))
suicide <- read_rds(here('data', 'cleaned_data', 'suicide.rds'))
pres_2016 <- read_rds(here('data', 'cleaned_data', 'pres_2016.rds'))
pres_2020 <- read_rds(here('data', 'cleaned_data', 'pres_2020.rds'))
covid_corrs <- read_rds(here('data', 'from_hpc', 'covid_corrs.rds'))
suicide_corrs <- read_rds(here('data', 'from_hpc', 'suicide_corrs.rds'))

@@

<https://journals.sagepub.com/doi/10.1177/0894439316631043> What
constructs might google trends capture and not capture well? Capture
attention but not attitudes

@@

```{r data-sources-table}
#| results='asis'

data_sources <- tibble::tribble(
~type, ~Validated.Data.Source, ~Type, ~Dates, ~Google.Trends.Used,
"Behaviors and Attitudes","General Social Survey", "Cross-Sectional", "2010 - 2020", NA,

"Behaviors and Attitudes","Vaccine Hesitancy for COVID-19", "Cross-Sectional", "March 3 – 15, 2021", "covid conspiracy', 'COVID-19 vaccine', 'Coronavirus', 'Covid-19'",

"Behaviors and Attitudes","Mask-Wearing Survey Data", "Cross-Sectional", "July 2 - 14, 2020", "'Face Mask', 'Mask', 'Cloth Face Mask'",

"Health","Covid Rates", "Longitudinal", "Every Monday, 2020 - 2021", "'Covid-19', 'Coronavirus', 'Taste Loss', 'Smell Loss'",

"Health","County Suicide Rates", "Longitudinal", "Yearly 2010-2020", "'Suicide', 'Depression',' Suicide Hotline'",

'Political',"American National Election Survey", "Cross-Sectional", "2020", NA,

'Political',"Presidential Election Results", "Cross Sectional", "2016 & 2020", "'Hilary Clinton', 'Donald Trump', 'Joe Biden'"
 ) %>% as_grouped_data(groups = c("type"), columns = NULL)

data_sources %>% 
  as_flextable(hide_grouplabel = TRUE) %>% 
  set_caption(caption = "New York Air Quality Measurements")  %>% 
  # theming
  theme_box() %>% 
  bg(bg = my_palette[8], part = "header") %>% 
  color(color = "white", part = "header") %>%
  set_table_properties(layout = "autofit", width = 1) %>% 
  # grouped row style
  fontsize(size = 8) %>% 
  bold(i = ~ !is.na(type), bold = TRUE) %>% 
  italic(i = ~ !is.na(type), italic = TRUE) %>% 
  bg(i = ~ !is.na(type), bg = "#bad7db", part = "body")

@@

One measure of attitudinal indicators is the Vaccine Hesitancy for COVID-19
[@vaches_data]. The CDC uses the U.S. Census Bureau’s Household Pulse Survey
(HPS) and the 2019 American Community Survey (ACS) 1-year Public Use Microdata
Sample (PUMS) to measure U.S. residents’ intentions to receive the COVID-19
vaccine if available during May 26, 2021 – June 7, 2021. This dataset consists
of `r nrow(vacc_hes)` observations, one for each U.S. County. The variable
measures the precent of adults in the county who describe themselves as
“unsure”, “probably not”, or “definitely not” going to get a COVID-19 vaccine
once one is available to them. The variable ranges from 
`r percent_format(0.01)(min(vacc_hes$vacc_hesitant))` to 
`r percent_format(0.01)(max(vacc_hes$vacc_hesitant))`.

Another attitudinal indicator I use is the Mask-Wearing Survey Data conducted by
Dynata for the New York Times from July 2 through 14, 2020 [@mask_data]. 250,000
survey respondents were asked, "How often do you wear a mask in public when you
expect to be within six feet of another person?". The NYT weighted each response
to create a county level measure of what percent of the county never, rarely,
sometimes, frequently, and always wore a mask when in public. This dataset
consists of `r nrow(mask)` observations, one for each U.S. County. This measure
represents the percent of adults in the county who never or rarely wear a mask
(range = `r percent_format(0.01)(min(mask$mask_rare))` to 
`r percent_format(0.01)(max(mask$mask_rare))`)

@@

I also use U.S. Covid-19 rates to validate health and disease related topics. I
retrieve U.S. county-level Covid-19 rates from by @covid_data, who compile this
data based on reports from state and local health agencies. It is widely
acknowledged that there are biases in this data due to inconsistencies and
availability in testing as well as different community propensity to test
[@gu22; @cdc20a] However, it is the best measure we have of actual case rates.
Case Rate is measured as number of cases per 100,000 population. Observations
vary from a minimum of 0 to a maximum of `r max(covid$covid_rate)` for each 
Monday from `r glue("{format( min(covid$date), '%B %d, %Y')} through {format(max(covid$date), '%B %d, %Y')}")`.
There are `r nrow(covid)` cases across `r nrow(count(covid, fips))` 
counties and `r nrow(count(covid, date))` dates. Missing data were interpolated 
using `zoo::na.approx()` [@zoo].

I also use county-level suicide rates from the US Centers for Disease Control
and Prevention [-@suic_data]. Data is grouped by year from 2010-2020. Raw death
rates are scaled by population size for each year and can be interpreted as the
death rate by suicide for every 1000 people. There are `r nrow(suicide)` total
cases, resulting from `r nrow(count(suicide, year))` observations of `r
nrow(count(suicide, fips))` counties. Missing data were interpolated using
`zoo::na.approx()` [@zoo]. Measures range from 
`r round(min(suicide$death_rate, na.rm=T),3)` to 
`r round(max(suicide$death_rate, na.rm=T),3)`.

### political
Finally, I test Google Trends as an operationalization of political
attitudes by first looking at actual voting outcomes in historical US
Presidential Election results. This data comes from @pres_data, who scraped the
results from Townhall.com, Fox News, Politico, and the New York Times. Data on 
presidential outcomes were avaiable for `r nrow(pres_2016)` counties in 2016 and
`r nrow(pres_2020)` counties in 2020. Each variable measures the percent of votes
for the candidate, with the lowest percent at 
`r percent_format(0.01)(min(pres_2020$biden_p, na.rm=T))`
and the highest at `r percent_format(0.01)(max(pres_2020$biden_p, na.rm=T))`.

@@

<!-- TODO: WHICH VARIABLES -->
<!-- TODO: VARIABLE SCALE -->

@@

In addition to specific outcomes of interest, I also gathered various county
controls to investigate possible variable confounding. The first Seven of these
variables come from the 2010-2019 5-year American Community Surveys [@acs2019;
@acs2018; @acs2017; @acs2016; @acs2015; @acs2014; @acs2013; @acs2012;
@acs2011; @acs2010]. These data include total population, population density,
unemployment rate for those 16 and over, median county income, average commute
time, percent of households living under the poverty line, and percent above 65
years old. In addition, some models employ the U.S. Current Population Survey &
American Community Survey Geographic Estimates of Internet Use, 1997-2018
[@internet_use] to estimate households with broadband internet subscriptions.
This final variable is an attempt to capture the latent propensity to use the
internet for information search.

@@

## Analysis
Google Search Trends data and additional demographic data are merged with each
individual indicator based on County FIPS Codes and date. After creating these
different datasets, I use the Pearson correlation formula (formula
\@ref(eq:pearsoncorr)) for cross-sectional numeric data to calculate the
strength of the relationship between each Google Trend and the respective
data source.

@@

To address longitudinal correlations, I employ Repeated Measures Correlation
using the `rmcorr` package in R [@bland1995; @bakdash2017]. Repeated Measures
Correlation is useful for determining the within-county association for paired
measures across time and counties. Results of these correlations can be seen in 
table \@ref(tab:corr-results).

As an additional test of the relationships, I employ multiple linear regression
(for cross-sectional datasets) and random intercept hierarchical linear models
[@pinheiro_etal21] (for longitudinal datasets) to identify the strength of
relationships across locales: I include city-data like county population size,
broadband rates, and median income to attempt to disentangle possible
confounders of the relationship between Google search Trends and verified
indicators. Identifying these possible confounded relationships will help to
explain why some articles find relationships between the trends and outcomes
while others did not. For linear regression models, I normalize independent
variables, i.e.variables have been centered and scaled to have a mean of 0 and
standard deviation 1.

@@

## Cultural
```{r corr-results}
#|  results='asis'

options(knitr.kable.NA = '')

table2 <- tribble(
  ~'grp', ~'variable', ~'measure',~'trend1', ~'trend2', ~'trend3', ~'trend4', 
  "Vaccine Hesitancy", NA,  NA, 'covid_conspiracy', 'covid_19_vaccine', 'coronavirus', 'covid_19', 
  "Vaccine Hesitancy", "Vaccine Hesitancy", "Pearson's R Correlation",
  as.character(round(cor(vacc_hes$vacc_hesitant, vacc_hes$covid_conspiracy, use = "complete.obs"),4)),
  as.character(round(cor(vacc_hes$vacc_hesitant, vacc_hes$covid_19_vaccine, use = "complete.obs"),4)),
  as.character(round(cor(vacc_hes$vacc_hesitant, vacc_hes$coronavirus, use = "complete.obs"),4)),
  as.character(round(cor(vacc_hes$vacc_hesitant, vacc_hes$covid_19, use = "complete.obs"),4)),

  "Mask Attitudes",NA,  NA, 'face_mask', 'mask', 'cloth_face_mask',  NA,
  "Mask Attitudes","Mask Rare", "Pearson's R Correlation",
  as.character(round(cor(mask$mask_rare, mask$face_mask, use = "complete.obs"),4)),
  as.character(round(cor(mask$mask_rare, mask$mask, use = "complete.obs"),4)),
  as.character(round(cor(mask$mask_rare, mask$cloth_face_mask, use = "complete.obs"), 4)), NA,

  "Covid Rates",NA,  NA, 'covid_19',  'smell_loss', 'taste_loss', NA, 
  "Covid Rates","Covid Rate", "Pearson's R Correlation", 
  as.character(round(cor(covid$covid_rate, covid$covid_19, use = "complete.obs"),4)),
  as.character(round(cor(covid$covid_rate, covid$smell_loss, use = "complete.obs"),4)),
  as.character(round(cor(covid$covid_rate, covid$taste_loss, use = "complete.obs"),4)),
  NA,
  "Covid Rates","Covid Rate", "rmcorr", 
  as.character(covid_corrs[[2,2]]), 
  as.character(covid_corrs[[2,3]]), 
  as.character(covid_corrs[[2,4]]), NA,

  "Suicide Rates",NA,  NA, 'suicide', 'depression', 'suicide_hotline', NA, 
  "Suicide Rates","Suicide Rate", "Pearson's R Correlation",
  as.character(round(cor(suicide$death_rate, suicide$suicide, use = "complete.obs"),4)),
  as.character(round(cor(suicide$death_rate, suicide$depression, use = "complete.obs"),4)),
  as.character(round(cor(suicide$death_rate, suicide$suicide_hotline, use = "complete.obs"),4)),
  NA,
  "Suicide Rates","Suicide Rate", "rmcorr", 
  as.character(suicide_corrs[[2,2]]), 
  as.character(suicide_corrs[[2,3]]), 
  as.character(suicide_corrs[[2,4]]), NA,

  "2016 Presidential Votes",NA,  NA, 'Hilary Clinton',  'Donald Trump', NA, NA,
  "2016 Presidential Votes","2016 Votes for Clinton", "Pearson's R Correlation",
  as.character(round(cor(pres_2016$clinton_p, pres_2016$`Hilary Clinton`, use = "complete.obs"),4)),
  as.character(round(cor(pres_2016$clinton_p, pres_2016$`Donald Trump`, use = "complete.obs"),4)), NA, NA,
  "2016 Presidential Votes","2016 Votes for Trump", "Pearson's R Correlation",
  as.character(round(cor(pres_2016$trump_p, pres_2016$`Hilary Clinton`, use = "complete.obs"),4)),
  as.character(round(cor(pres_2016$trump_p, pres_2016$`Donald Trump`, use = "complete.obs"),4)), NA, NA,

  "2016 Presidential Votes",NA,  NA, 'Joe Biden',  'Donald Trump', NA, NA,
  "2016 Presidential Votes","2020 Votes for Biden", "Pearson's R Correlation",
  as.character(round(cor(pres_2020$biden_p, pres_2020$`Joe Biden`, use = "complete.obs"),4)),
  as.character(round(cor(pres_2020$biden_p, pres_2020$`Donald Trump`, use = "complete.obs"),4)), NA, NA,
  "2016 Presidential Votes","2020 Votes for Trump", "Pearson's R Correlation",
  as.character(round(cor(pres_2020$trump_p, pres_2020$`Joe Biden`, use = "complete.obs"),4)),
  as.character(round(cor(pres_2020$trump_p, pres_2020$`Donald Trump`, use = "complete.obs"),4)), NA, NA
)  %>%   
  select(grp, measure, variable, trend1, trend2, trend3, trend4) %>% 
  as_grouped_data(groups = c("grp"), columns = NULL)

as_flextable(table2, hide_grouplabel = TRUE) %>% 
  set_caption(caption = "Correlation Results")  %>% 
  # theming
  theme_box() %>% 
  bg(bg = my_palette[8], part = "header") %>% 
  color(color = "white", part = "header") %>%
  set_table_properties(layout = "autofit", width = 1) %>% 
  # grouped row style
  fontsize(size = 8) %>% 
  bold(i = ~ !is.na(grp), bold = TRUE) %>% 
  italic(i = ~ !is.na(grp), italic = TRUE) %>% 
  bg(i = ~ !is.na(grp), bg = "#bad7db", part = "body")
```

The first attitudinal indicators is Vaccine Hesitancy for COVID-19 vaccines
[@vaches_data]. When comparing the measure of vaccine hesitancy to four
different Google Search Trends, the correlation does not exceed -0.4021
('Coronavirus' and vaccine hesitancy). Correlation's under |0.40| are considered
to be weak according to the common rules of thumb. When running these
correlations in multiple linear regression (see the results in table 
\@ref(tab:vacc_hes_analysis)), I see an $r^2$ of 0.221 (Model 1)
and 0.346 (Model 2), indicating that the Google Trends are able to explain about
22% of the variation in Vaccine Hesitancy alone. Demographic characteristics
like the percentage of households with broadband internet and the population
density are able to explain about 35% of the variation (model 3), outperforming
the first two models. The Trend coefficients themselves, however, are
significant and remain significant when controlling for demographics. This
reinforces the finding from the Pearson Correlation that there is a significant
but weak relationship between the Google Trends and Vaccine Hesitancy.

```{r vacc_hes_analysis}
#| tab.cap = "Linear Regression Results for Vaccine Hesitancy",
#|  results='asis'

vacc_hes <- vacc_hes %>% 
  select(-c(DMA_google, Geo_QName)) %>% 
  mutate(across(covid_conspiracy:broadband  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))

@@

modelsummary(list(vacc_hes_2, vacc_hes_2b, vacc_hes_1, vacc_hes_3), 
             # title = "Linear Regression Results for Vaccine Hesitancy",
             notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).'),
             estimate = "{estimate}{stars}",
             gof_omit = 'AIC|BIC|ICC|RMSE'
             ) %>%
  kable_styling(latex_options = c("hold_position", 'condensed'),
                font_size = 8)

@@

The second attitudinal measure I test is how Google Trends relates to rare mask
usage. As with vaccine hesitancy, the Pearson correlations are weak, if not 
negligible. I introduce these trends in multiple linear regression in table 
\@ref(tab:mask_analysis). Model 1 demonstrates that these three Google Search
Trends can explain about 9% of the variance in mask usage across U.S. counties,
reinforcing the conclusion that the relationship is quite weak. The coefficients
themselves are somewhat significant in Model 1. However, after including the
demographic varaibles in Models 2 and 3, we see that the relationship between
the Google Search Trends and mask usage is strengthed in magnitude and in
significance, likely indicating a repression effect due to background
relationships between the trends and demograhic variables. While the trends are
significant and match the magnitude of the demographic variables, the low $r^2$ 
for the trends still provides evidence that Google Search Trends data cannot 
replace survey analysis when trying to measure rare mask usage.

```{r mask_analysis}
#|  results='asis',
#| tab.cap = "Linear Regression Results for Rare Mask Usage"

mask <- mask %>% 
  select(-c(DMA_google, Geo_QName)) %>% 
  mutate(across(face_mask:broadband  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))

@@

modelsummary(list(mask_2, mask_1, mask_3), 
             # title = "Linear Regression Results for Rare Mask Usage",
             notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).'),
             estimate = "{estimate}{stars}",
             gof_omit = 'AIC|BIC|ICC|RMSE') %>%
  kable_styling(latex_options = c("hold_position", 'condensed'),
                font_size = 8)

@@

```{r covid_analysis}
covid <- covid %>% 
  select(-c(dma_google, Geo_QName, county, state)) %>% 
  mutate(across(covid_19:broadband  , ~ scale(.x, center=TRUE, scale=TRUE)[,1])) %>% 
  left_join(covid %>%
              group_by(fips) %>%
              summarize(covid_rate_fips_mean = mean(covid_rate, na.rm = TRUE)),
            by = "fips") %>% 
  drop_na(covid_rate)

@@

modelsummary(list(covid_2, covid_1, covid_3), 
             # title = "Hierarchical Model for Covid Case Rates",
             notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
                      'Random intercept per county'),
             estimate = "{estimate}{stars}",
             gof_omit = 'AIC|BIC|ICC|RMSE') %>%
  kable_styling(latex_options = c("hold_position", 'condensed'),
                font_size = 8)

@@

```{r suicide_analysis}
suicide <- suicide %>% 
  select(-c(dma_google, Geo_QName, county, population, deaths)) %>% 
  mutate(across(suicide:broadband  , ~ scale(.x, center=TRUE, scale=TRUE)[,1])) %>% 
  left_join(suicide %>%
              group_by(fips) %>%
              summarize(death_rate_fips_mean = mean(death_rate , na.rm = TRUE)),
            by = "fips") %>% 
  drop_na(death_rate )

@@

modelsummary(list(suicide_2, suicide_1, suicide_3), 
             # title = "Hierarchical Model for Suicide Rates",
             notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
                      'Random intercept per county'),
             estimate = "{estimate}{stars}",
             gof_omit = 'AIC|BIC|ICC|RMSE') %>%
  kable_styling(latex_options = c("hold_position", 'condensed'),
                font_size = 8)

@@

```{r pres_2016_analysis}
pres_2016 <- pres_2016 %>% 
  select(-c(Geo_QName, dma)) %>% 
  mutate(across(c(`Hilary Clinton`,`Donald Trump`:broadband)  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))

@@

```{r pres_2020_analysis}
pres_2020 <- pres_2020 %>% 
  select(-c(Geo_QName, dma)) %>% 
  mutate(across(c(`Joe Biden`,`Donald Trump`:broadband)  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))
